### 2019-11-21 3_implementation.tex
Update reference to supplemental material.
combine ompss with openmp

We have implemented Task Bench in the 15 parallel and distributed
programming systems listed in Table~\ref{tab:systems}. These include
traditional HPC programming models: MPI~\cite{MPI} (with bulk
synchronous and point-to-point communication) and MPI+X (with OpenMP
and CUDA); PGAS and actor models: Chapel~\cite{Chapel15},
Charm++~\cite{Charmpp93}, X10~\cite{X1005}; and newer task-based
systems: OmpSs~\cite{OmpSs11}, OpenMP~\cite{OpenMPSpec40} (with task
dependencies), PaRSEC (with \emph{parameterized task graphs}
(PTG)~\cite{PARSEC13} and \emph{dynamic task discovery}
(DTD)~\cite{PARSEC_DTD}), Realm~\cite{Realm14},
Regent~\cite{Regent15}, and StarPU~\cite{StarPU11}. Also, we consider
several systems used in large scale data analytics and workflows:
Dask~\cite{Dask15}, Spark~\cite{Spark10}, Swift/T~\cite{Wozniak13},
and TensorFlow~\cite{TensorFlow15}. We describe the systems, and any
salient details of their Task Bench implementations, in our
supplemental material.

@@

\subsection{OmpSs}

OmpSs~\cite{OmpSs11} is a programming model for loop- and task-based parallelism
that is source-compatible with OpenMP. Our Task Bench implementation
uses OpenMP 4.0-style task dependencies. Because OpenMP tasks have a fixed number of dependencies, we use a switch
statement to implement the dynamic dependencies required for Task
Bench. The implementation is otherwise straightforward.

@@

\subsection{OpenMP}

OpenMP~\cite{OpenMPSpec40} is the industry standard API for loop-based
parallelism on shared-memory systems, and supports task dependencies as of version 4.0. Our Task Bench implementation
for OpenMP is similar to OmpSs and uses
task dependencies. We tested with GNU GOMP and Intel KMP
and found KMP to be better performing.

>>>>

We have implemented Task Bench in the 15 parallel and distributed
programming systems listed in Table~\ref{tab:systems}. These include
traditional HPC programming models: MPI~\cite{MPI} (with bulk
synchronous and point-to-point communication) and MPI+X (with OpenMP
and CUDA); PGAS and actor models: Chapel~\cite{Chapel15},
Charm++~\cite{Charmpp93}, X10~\cite{X1005}; and newer task-based
systems: OmpSs~\cite{OmpSs11}, OpenMP~\cite{OpenMPSpec40} (with task
dependencies), PaRSEC (with \emph{parameterized task graphs}
(PTG)~\cite{PARSEC13} and \emph{dynamic task discovery}
(DTD)~\cite{PARSEC_DTD}), Realm~\cite{Realm14},
Regent~\cite{Regent15}, and StarPU~\cite{StarPU11}. Also, we consider
several systems used in large scale data analytics and workflows:
Dask~\cite{Dask15}, Spark~\cite{Spark10}, Swift/T~\cite{Wozniak13},
and TensorFlow~\cite{TensorFlow15}. We describe the systems, and any
salient details of their Task Bench implementations, below.

@@

\subsection{OmpSs/OpenMP}

OmpSs~\cite{OmpSs11} is a programming model for loop- and task-based parallelism
that is source-compatible with OpenMP. Our Task Bench implementation
uses OpenMP 4.0-style~\cite{OpenMPSpec40} task dependencies. 
Because OpenMP tasks have a fixed number of dependencies, we use a switch
statement to implement the dynamic dependencies required for Task
Bench. The implementation is otherwise straightforward. 
The Task Bench implementation for OpenMP is similar to OmpSs.
We tested with GNU GOMP and Intel KMP and found KMP to be better performing.

@@

%\subsection{OpenMP}

%OpenMP~\cite{OpenMPSpec40} is the industry standard API for loop-based
%parallelism on shared-memory systems, and supports task dependencies as of version 4.0. Our Task Bench implementation
%for OpenMP is similar to OmpSs and uses
%task dependencies. We tested with GNU GOMP and Intel KMP
%and found KMP to be better performing.
